Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2017-11-14 inst/examples/20170201-manuscript.Rmd
ok

### Fig. 1: Number of publication places over time

@@

### Fig. 7: Publishing activity and riksdagar: Kungliga

@@

### Fig. 12: Title count per capita

@@

### Fig. 13: Title count (absolute)

@@

### Fig. 14: Octavo paper consumption

@@

### Fig. 15: Octavo title length (word count)

@@

### Fig. 17: Topic richness per language (Fennica)

@@

### Fig. 18: Temporary sermons in Latin and Swedish

@@

### Fig. 19: Devotional literature (catechisms, hymns, prayers, etc.)

>>>>

### Fig 1: Number of publication places over time

@@

### Fig 7: Publishing activity and riksdagar: Kungliga

@@

### Fig 12: Title count per capita

@@

### Fig 13: Title count (absolute)

@@

### Fig 14: Octavo paper consumption

@@

### Fig 15: Octavo title length (word count)

@@

### Fig 17: Topic richness per language (Fennica)

@@

### Fig 18: Temporary sermons in Latin and Swedish

@@

### Fig 19: Devotional literature (catechisms, hymns, prayers, etc.)
